Measuring the Inherent Readability of Five Common Programming Languages

### 2015-03-16 rmtw/a1/assignment_1.tex
Added group 9 review for assignment 5

\SubSection{Threats to Validity}
As in all research there are threats to the validity of the study being undertaken. Our largest threat would be the external validity of the data collected. The students were selected from the three current years studying at the University of Gothenburg. Most of the respondents indicated that they are in the first year of their studies and as such their inexperience could be a limiting factor on their answers to the survey. The students may also have had a bias for one of the languages; Java. So far, the students in the first year have been formally taught in only Java. This means that there is a lower chance they would be familiar with reading other language syntax other than Java and as such they would be more likely to see Java favourably than others. We cannot therefore generalise that Java has higher readability than that of the other languages despite what the results show.

>>>>

\SubSection{Threats to Validity}
As in all research there are threats to the validity of the study being undertaken. The comparison of the perceived readability of programming languages cannot be fully determined from a single study, as such, more are required to make more concrete generalisations. Given this, the threats to internal and construct validity are among the most important for this study. The most import however would be the external validity of the study.

The students were selected from the three current years studying at the University of Gothenburg. Most of the respondents indicated that they are in the first year of their studies and as such their inexperience could be a limiting factor on their answers to the survey. The students may also have had a bias for one of the languages; Java. So far, the students in the first year have been formally taught in only Java. This means that there is a lower chance they would be familiar with reading other language syntax other than Java and as such they would be more likely to see Java favourably than others. We cannot therefore generalise that Java has higher readability than that of the other languages despite what the results show.
